\documentclass[11pt]{article}
\include{noteinclude}
\usepackage{supertabular}

\begin{document}

\tablecaption{Photodissociation and photoionization reactions \\}
\tablehead{\textbf{Species} & \textbf{Reaction} & \textbf{Source} \\ \hline }
\tabletail{\hline \multicolumn{3}{r}{\emph{Continued on next page}}\\}
\tablelasttail{\hline}
\begin{supertabular}{ccl}
AlO & AlO +  photon  \rarrow\  Al +  O & Berezhnoy \& Klumov 2008 \\
C & C +  photon  \rarrow\  C$^+$ +  e & Huebner et al. 1992 \\
C & C +  photon  \rarrow\  C$^+$ +  e & Huebner \& Mukherjee 2011 \\
CH$_4$ & CH$_4$ +  photon  \rarrow\  CH +  H$_2$ & Huebner \& Mukherjee 2011 \\
CH$_4$ & CH$_4$ +  photon  \rarrow\  CH +  H$_2$ & Huebner et al. 1992 \\
CH$_4$ & CH$_4$ +  photon  \rarrow\  CH$_2$ +  H & Huebner \& Mukherjee 2011 \\
CH$_4$ & CH$_4$ +  photon  \rarrow\  CH$_2$ +  H & Huebner et al. 1992 \\
CH$_4$ & CH$_4$ +  photon  \rarrow\  CH$_2$ +  H$_2$ & Huebner et al. 1992 \\
CH$_4$ & CH$_4$ +  photon  \rarrow\  CH$_2$ +  H$_2$ & Huebner \& Mukherjee 2011 \\
CH$_4$ & CH$_4$ +  photon  \rarrow\  CH$_3$ +  H & Huebner \& Mukherjee 2011 \\
CH$_4$ & CH$_4$ +  photon  \rarrow\  CH$_3$ +  H & Huebner et al. 1992 \\
CH$_4$ & CH$_4$ +  photon  \rarrow\  CH$_3$ +  H$^+$ & Huebner et al. 1992 \\
CH$_4$ & CH$_4$ +  photon  \rarrow\  CH$_3$ +  H$^+$ & Huebner \& Mukherjee 2011 \\
CH$_4$ & CH$_4$ +  photon  \rarrow\  CH$_4$$^+$ +  e & Huebner et al. 1992 \\
CH$_4$ & CH$_4$ +  photon  \rarrow\  CH$_4$$^+$ +  e & Huebner \& Mukherjee 2011 \\
CH$_4$ & CH$_4$ +  photon  \rarrow\  H +  CH$_3$$^+$ & Huebner \& Mukherjee 2011 \\
CH$_4$ & CH$_4$ +  photon  \rarrow\  H +  CH$_3$$^+$ & Huebner et al. 1992 \\
CH$_4$ & CH$_4$ +  photon  \rarrow\  H$_2$ +  CH$_2$$^+$ & Huebner et al. 1992 \\
CH$_4$ & CH$_4$ +  photon  \rarrow\  H$_2$ +  CH$_2$$^+$ & Huebner \& Mukherjee 2011 \\
CH$_4$ & CH$_4$ +  photon  \rarrow\  H$_2$ +  CH$_2$ & Huebner et al. 1992 \\
CH$_4$ & CH$_4$ +  photon  \rarrow\  H$_2$ +  H & Huebner et al. 1992 \\
CH$_4$ & CH$_4$ +  photon  \rarrow\  H$_2$ +  H & Huebner \& Mukherjee 2011 \\
CO$_2$ & CO$_2$ +  photon  \rarrow\  CO +  O & Huebner et al. 1992 \\
CO$_2$ & CO$_2$ +  photon  \rarrow\  CO +  O & Huebner \& Mukherjee 2011 \\
CO$_2$ & CO$_2$ +  photon  \rarrow\  CO +  O$^+$ & Huebner et al. 1992 \\
CO$_2$ & CO$_2$ +  photon  \rarrow\  CO +  O$^+$ & Huebner \& Mukherjee 2011 \\
CO$_2$ & CO$_2$ +  photon  \rarrow\  CO$_2$$^+$ +  e & Huebner \& Mukherjee 2011 \\
CO$_2$ & CO$_2$ +  photon  \rarrow\  CO$_2$$^+$ +  e & Huebner et al. 1992 \\
CO$_2$ & CO$_2$ +  photon  \rarrow\  O +  CO$^+$ & Huebner et al. 1992 \\
CO$_2$ & CO$_2$ +  photon  \rarrow\  O +  CO$^+$ & Huebner \& Mukherjee 2011 \\
CO$_2$ & CO$_2$ +  photon  \rarrow\  O$_2$ +  C$^+$ & Huebner et al. 1992 \\
CO$_2$ & CO$_2$ +  photon  \rarrow\  O$_2$ +  C$^+$ & Huebner \& Mukherjee 2011 \\
Ca & Ca +  photon  \rarrow\  Ca$^+$ +  e & Huebner et al. 1992 \\
Ca & Ca +  photon  \rarrow\  Ca$^+$ +  e & Huebner \& Mukherjee 2011 \\
Ca(OH)$_2$ & Ca(OH)$_2$ +  photon  \rarrow\  CaOH +  OH & Berezhnoy 2013 \\
CaO & CaO +  photon  \rarrow\  Ca +  O & Berezhnoy 2013 \\
CaO & CaO +  photon  \rarrow\  Ca +  O & Berezhnoy \& Klumov 2008 \\
CaOH & CaOH +  photon  \rarrow\  Ca +  OH & Berezhnoy 2013 \\
CaOH & CaOH +  photon  \rarrow\  CaO +  H & Berezhnoy 2013 \\
Cl & Cl +  photon  \rarrow\  Cl$^+$ +  e & Huebner et al. 1992 \\
Cl & Cl +  photon  \rarrow\  Cl$^+$ +  e & Huebner \& Mukherjee 2011 \\
FeO & FeO +  photon  \rarrow\  Fe +  O & Berezhnoy \& Klumov 2008 \\
H & H +  photon  \rarrow\  H$^+$ +  e & Huebner et al. 1992 \\
H & H +  photon  \rarrow\  H$^+$ +  e & Huebner \& Mukherjee 2011 \\
H$_2$ & H$_2$ +  photon  \rarrow\  H +  H & Huebner \& Mukherjee 2011 \\
H$_2$ & H$_2$ +  photon  \rarrow\  H +  H & Huebner et al. 1992 \\
H$_2$ & H$_2$ +  photon  \rarrow\  H +  H$^+$ & Huebner et al. 1992 \\
H$_2$ & H$_2$ +  photon  \rarrow\  H +  H$^+$ & Huebner \& Mukherjee 2011 \\
H$_2$ & H$_2$ +  photon  \rarrow\  H$_2$$^+$ +  e & Huebner \& Mukherjee 2011 \\
H$_2$ & H$_2$ +  photon  \rarrow\  H$_2$$^+$ +  e & Huebner et al. 1992 \\
H$_2$O & H$_2$O +  photon  \rarrow\  H +  H & Huebner \& Mukherjee 2011 \\
H$_2$O & H$_2$O +  photon  \rarrow\  H +  H & Huebner et al. 1992 \\
H$_2$O & H$_2$O +  photon  \rarrow\  H +  OH$^+$ & Huebner et al. 1992 \\
H$_2$O & H$_2$O +  photon  \rarrow\  H +  OH$^+$ & Huebner \& Mukherjee 2011 \\
H$_2$O & H$_2$O +  photon  \rarrow\  H$_2$ +  O & Huebner et al. 1992 \\
H$_2$O & H$_2$O +  photon  \rarrow\  H$_2$ +  O & Huebner \& Mukherjee 2011 \\
H$_2$O & H$_2$O +  photon  \rarrow\  H$_2$ +  O$^+$ & Huebner et al. 1992 \\
H$_2$O & H$_2$O +  photon  \rarrow\  H$_2$ +  O$^+$ & Huebner \& Mukherjee 2011 \\
H$_2$O & H$_2$O +  photon  \rarrow\  H$_2$O$^+$ +  e & Huebner et al. 1992 \\
H$_2$O & H$_2$O +  photon  \rarrow\  H$_2$O$^+$ +  e & Huebner \& Mukherjee 2011 \\
H$_2$O & H$_2$O +  photon  \rarrow\  OH +  H & Huebner \& Mukherjee 2011 \\
H$_2$O & H$_2$O +  photon  \rarrow\  OH +  H & Huebner et al. 1992 \\
H$_2$O & H$_2$O +  photon  \rarrow\  OH +  H$^+$ & Huebner et al. 1992 \\
H$_2$O & H$_2$O +  photon  \rarrow\  OH +  H$^+$ & Huebner \& Mukherjee 2011 \\
He & He +  photon  \rarrow\  He$^+$ +  e & Huebner et al. 1992 \\
He & He +  photon  \rarrow\  He$^+$ +  e & Huebner \& Mukherjee 2011 \\
K & K +  photon  \rarrow\  K$^+$ +  e & Huebner et al. 1992 \\
K & K +  photon  \rarrow\  K$^+$ +  e & Huebner \& Mukherjee 2011 \\
KO & KO +  photon  \rarrow\  K +  O & Berezhnoy \& Klumov 2008 \\
Mg & Mg +  photon  \rarrow\  Mg$^+$ +  e & Huebner \& Mukherjee 2011 \\
Mg & Mg +  photon  \rarrow\  Mg$^+$ +  e & Huebner et al. 1992 \\
MgO & MgO +  photon  \rarrow\  Mg +  O & Berezhnoy \& Klumov 2008 \\
N & N +  photon  \rarrow\  N$^+$ +  e & Huebner \& Mukherjee 2011 \\
N & N +  photon  \rarrow\  N$^+$ +  e & Huebner et al. 1992 \\
NH$_3$ & NH$_3$ +  photon  \rarrow\  H +  NH$_2$$^+$ & Huebner \& Mukherjee 2011 \\
NH$_3$ & NH$_3$ +  photon  \rarrow\  H +  NH$_2$$^+$ & Huebner et al. 1992 \\
NH$_3$ & NH$_3$ +  photon  \rarrow\  H$_2$ +  H & Huebner \& Mukherjee 2011 \\
NH$_3$ & NH$_3$ +  photon  \rarrow\  H$_2$ +  H & Huebner et al. 1992 \\
NH$_3$ & NH$_3$ +  photon  \rarrow\  H$_2$ +  NH$^+$ & Huebner \& Mukherjee 2011 \\
NH$_3$ & NH$_3$ +  photon  \rarrow\  H$_2$ +  NH$^+$ & Huebner et al. 1992 \\
NH$_3$ & NH$_3$ +  photon  \rarrow\  NH +  H & Huebner et al. 1992 \\
NH$_3$ & NH$_3$ +  photon  \rarrow\  NH +  H & Huebner \& Mukherjee 2011 \\
NH$_3$ & NH$_3$ +  photon  \rarrow\  NH +  H$_2$ & Huebner et al. 1992 \\
NH$_3$ & NH$_3$ +  photon  \rarrow\  NH +  H$_2$ & Huebner \& Mukherjee 2011 \\
NH$_3$ & NH$_3$ +  photon  \rarrow\  NH$_2$ +  H & Huebner et al. 1992 \\
NH$_3$ & NH$_3$ +  photon  \rarrow\  NH$_2$ +  H & Huebner \& Mukherjee 2011 \\
NH$_3$ & NH$_3$ +  photon  \rarrow\  NH$_2$ +  H$^+$ & Huebner et al. 1992 \\
NH$_3$ & NH$_3$ +  photon  \rarrow\  NH$_2$ +  H$^+$ & Huebner \& Mukherjee 2011 \\
NH$_3$ & NH$_3$ +  photon  \rarrow\  NH$_3$$^+$ +  e & Huebner et al. 1992 \\
NH$_3$ & NH$_3$ +  photon  \rarrow\  NH$_3$$^+$ +  e & Huebner \& Mukherjee 2011 \\
N$_2$ & N$_2$ +  photon  \rarrow\  N +  N & Huebner et al. 1992 \\
N$_2$ & N$_2$ +  photon  \rarrow\  N +  N & Huebner \& Mukherjee 2011 \\
N$_2$ & N$_2$ +  photon  \rarrow\  N +  N$^+$ & Huebner \& Mukherjee 2011 \\
N$_2$ & N$_2$ +  photon  \rarrow\  N +  N$^+$ & Huebner et al. 1992 \\
N$_2$ & N$_2$ +  photon  \rarrow\  N$_2$$^+$ +  e & Huebner et al. 1992 \\
N$_2$ & N$_2$ +  photon  \rarrow\  N$_2$$^+$ +  e & Huebner \& Mukherjee 2011 \\
Na & Na +  photon  \rarrow\  Na$^+$ +  e & Huebner et al. 1992 \\
Na & Na +  photon  \rarrow\  Na$^+$ +  e & Huebner \& Mukherjee 2011 \\
O & O +  photon  \rarrow\  O$^+$ +  e & Huebner \& Mukherjee 2011 \\
O & O +  photon  \rarrow\  O$^+$ +  e & Huebner et al. 1992 \\
OH & OH +  photon  \rarrow\  O +  H & Huebner \& Mukherjee 2011 \\
OH & OH +  photon  \rarrow\  O +  H & Huebner et al. 1992 \\
OH & OH +  photon  \rarrow\  OH$^+$ +  e & Huebner et al. 1992 \\
OH & OH +  photon  \rarrow\  OH$^+$ +  e & Huebner \& Mukherjee 2011 \\
O$_2$ & O$_2$ +  photon  \rarrow\  O +  O & Huebner et al. 1992 \\
O$_2$ & O$_2$ +  photon  \rarrow\  O +  O & Huebner \& Mukherjee 2011 \\
O$_2$ & O$_2$ +  photon  \rarrow\  O +  O$^+$ & Huebner et al. 1992 \\
O$_2$ & O$_2$ +  photon  \rarrow\  O +  O$^+$ & Huebner \& Mukherjee 2011 \\
O$_2$ & O$_2$ +  photon  \rarrow\  O$_2$$^+$ +  e & Huebner \& Mukherjee 2011 \\
O$_2$ & O$_2$ +  photon  \rarrow\  O$_2$$^+$ +  e & Huebner et al. 1992 \\
S & S +  photon  \rarrow\  S$^+$ +  e & Huebner \& Mukherjee 2011 \\
S & S +  photon  \rarrow\  S$^+$ +  e & Huebner et al. 1992 \\
SO & SO +  photon  \rarrow\  S +  O & Huebner et al. 1992 \\
SO & SO +  photon  \rarrow\  S +  O & Huebner \& Mukherjee 2011 \\
SO & SO +  photon  \rarrow\  SO$^+$ +  e & Huebner et al. 1992 \\
SO & SO +  photon  \rarrow\  SO$^+$ +  e & Huebner \& Mukherjee 2011 \\
SO$_2$ & SO$_2$ +  photon  \rarrow\  S$^+$ +  O$_2$ & Huebner \& Mukherjee 2011 \\
SO$_2$ & SO$_2$ +  photon  \rarrow\  S$^+$ +  O$_2$ & Huebner et al. 1992 \\
SO$_2$ & SO$_2$ +  photon  \rarrow\  SO +  O & Huebner et al. 1992 \\
SO$_2$ & SO$_2$ +  photon  \rarrow\  SO +  O & Huebner \& Mukherjee 2011 \\
SO$_2$ & SO$_2$ +  photon  \rarrow\  SO$_2$$^+$ +  e & Huebner \& Mukherjee 2011 \\
SO$_2$ & SO$_2$ +  photon  \rarrow\  SO$_2$$^+$ +  e & Huebner et al. 1992 \\
SiO & SiO +  photon  \rarrow\  Si +  O & Berezhnoy \& Klumov 2008 \\
TiO & TiO +  photon  \rarrow\  Ti +  O & Berezhnoy \& Klumov 2008 \\
\end{supertabular}

\end{document}
