\documentclass[11pt]{article}
\include{noteinclude}

\begin{document}
\section{Default Formatfiles}
\begin{enumerate}
\item Images: These are default files for makeing model images. Replace 'SS' with the 
species: `Na', `Ca', or `Mg'
  \begin{itemize}
  \item \texttt{Mercury.SS.image.xy.wid6.format}: Image of equatorial plane (view from 
  above north pole) from $\pm3$ \Rmerc\ in each direction.
  \item \texttt{Mercury.SS.image.xz.wid6.format}: Image of noon-midnight plane (view 
  from above dawn point) $\pm3$ \Rmerc\ in each direction.
  \item \texttt{Mercury.SS.image.yz.wid6.format}: Image of Dawn-Dusk plane (view from
  sun) from $\pm3$ \Rmerc\ in each direction.
  \end{itemize}

\item MASCS Simulations: These are default files from simulating the MASCS 
lines-of-sight. Replace `SS' with the species: `Na', `Ca', or `Mg'. Replace `XXXX' with
the four digit orbit number. Orbit 33 is `0033'.
  \begin{itemize}
  \item \texttt{MESSENGER.OrbitXXXX.SS.dphi1.format}: cone with opening 1\degr.
  \item \texttt{MESSENGER.OrbitXXXX.SS.dphi3.format}: cone with opening 3\degr.
  \item \texttt{MESSENGER.OrbitXXXX.SS.dr0p05.format}: cylinder of width 0.05 \Rmerc.
  \item \texttt{MESSENGER.OrbitXXXX.SS.dr0p1.format}: cylinder of width 0.1 \Rmerc.
  \end{itemize}

\item I can create more default files on request.
\end{enumerate}

\section{Using these files}

\begin{enumerate}
\item Basic usage with no changes.
\begin{verbatim}
IDL> formatfile = 'MESSENGER.Orbit0022.Ca.dphi3.format'
IDL> result = produce_results(inputfile, formatfile)
\end{verbatim}
It is not necessary to specify the path. If the given formatfile is not found in the
current directory, the program searches a default path.

\item To make a change:
\begin{verbatim}
IDL> formatfile = 'MESSENGER.Orbit0022.Ca.dphi3.format'
IDL> format = read_resultformat(formatfile)
IDL> format.geometry.dphi = 1*!dtor  ;; use a 1 degree cone angle
IDL> result = produce_results(inputfile, format)
\end{verbatim}
The function \textit{produce\_results} can take either a file name or a format structure
as an input.
\end{enumerate}

\end{document}
